Paper Figures

### 2019-08-12 PaperFigures.Rmd
with plots for all 6 groups but TB got messed up

---
title: "Paper Figures"
author: "Taryn McLaughlin"
date: "7/29/2019"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, comment=NA, warning=FALSE, echo=FALSE)
library(dplyr)
library(knitr)
library(ggplot2)
library(gridExtra)
library(GGally)
library(ggpubr)
library(cowplot)
library(tidyr)
library(reshape2)
library(cowplot)
library(corrplot)
library(sjPlot)
```

@@

baseplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    geom_point(shape=16,size=2, position = position_jitterdodge(dodge.width=1))+
    scale_fill_manual(values = colors)+
    theme_classic()+ theme(legend.position="none")+
    theme(text = element_text(size=20))+
    theme(plot.subtitle = element_text(hjust = 0.5)) +
    stat_compare_means(aes(label = sprintf("p = %5.3f", as.numeric(..p.format..))),
                       label.y= (max(data[,yval], na.rm = TRUE)*1.1), label.x=1.3,
                       size=6)+
    labs(x="")
}

booleanplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    geom_point(shape=16,size=2, position = position_jitterdodge(dodge.width=1))+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none")+
    theme(text = element_text(size=20))+
    theme(plot.subtitle = element_text(hjust = 0.5)) +
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=8)+
    labs(x="")
}

healthy.cols<- c("SM+" = "#1a9850", "SM-" ="#91cf60")
ltbi.cols<- c("SM+" = "#2166ac", "SM-" = "#85ABD1")
tb.cols<- c("SM+" = "#b2182b", "SM-"="#E59EA6")
```

@@

#Healthy Adults
####The frequency of T-bet+ CD4+ T cells is lower amongst SM+ Healthy Adults  
```{r, fig.height=6, fig.width=3}
cd4<-filter_hc(subset(CD4, CD4$Stim=="UN"))
cyt<-filter_hc(subset(CYT, CYT$Stim=="PMA"))
phen<-filter_hc(subset(PHEN, PHEN$Stim=="PMA"))
og<-filter_hc(subset(OG, OG$Stim=="SEB"))
ogphen<-filter_hc(subset(OGPHEN, OGPHEN$Stim=="SEB"))
baseplot(cd4, "SM", "T-bet", healthy.cols)+labs(y="Frequency T-bet+ CD4+ T cells (%)")
```

####Generic cytokine production from CD4+ T cells stimulated with PMA & Ionomycin does not differ between SM- and SM+ Healthy Adults
```{r, fig.height=6, fig.width=10}
melt<-melt(cyt, id.vars=c("TB","SM"), measure.vars=c("Cyt.Freq", "TH1.Freq", "TH1.2.Freq", "TH2.Freq"))
cyt_groups <- as_labeller(c("Cyt.Freq" = "Total", "TH1.Freq" = "TH1", 
                    "TH1.2.Freq" = "TH1/2", "TH2.Freq" = "TH2"))
baseplot(melt, "SM", "value", healthy.cols)+
    facet_wrap(~variable, ncol=4, labeller=cyt_groups)+
    labs(y="Frequency of Cytokine+ CD4+ T cells (%)")
```

@@

```{r, fig.height=10, fig.width=8}
test<-melt(phen, id.vars=c("TB", "SM"), 
           measure.vars=c("TH1_T-bet", "TH1_GATA3", "TH1_CXCR3", "TH1_CCR4",
           "TH2_T-bet", "TH2_GATA3", "TH2_CXCR3", "TH2_CCR4"))

test$subset<-tstrsplit(test$variable, "_")[[1]]
test$subset<-paste(test$subset, "Cytokine+ CD4+ T Cells", sep=" ")
test$variable<-gsub("TH1_","", test$variable)
test$variable<-gsub("TH2_","", test$variable)
test$variable<-factor(test$variable, levels=c("T-bet", "GATA3", "CXCR3", "CCR4"))

@@

```{r, fig.height=8, fig.width=10}
booleanplot(test, "SM","value", healthy.cols)+
    facet_grid(subset~variable, scales="free")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    labs(y="Frequency of Marker+ CD4+ T cells (%)")
```

#QFT+

####QFT+ individuals coinfected with S. mansoni have higher Mtb peptide-specific total cytokine production, specifically due to higher co-production of IFNγ and TNFa
```{r, fig.height=6, fig.width=10}
cyt<-filter_ltbi(subset(CYT, CYT$Stim=="PEP"))
phen<-filter_ltbi(subset(PHEN, PHEN$Stim=="PEP"))
og<-filter_ltbi(subset(OG, OG$Stim=="PEP"))
ogphen<-filter_ltbi(subset(OGPHEN, OGPHEN$Stim=="PEP"))
oggt<-filter_ltbi(subset(OG.GT, OG.GT$Stim=="PEP"))

#generate cytokine table for graphing
melt<-melt(cyt, 
    id.vars=c("TB","SM"), 
    measure.vars=c("Cyt.Freq", "TH1.Freq", "TH1.2.Freq", "TH2.Freq", "G_x_x_T"))
cyt_groups <- as_labeller(c("Cyt.Freq" = "Total", "TH1.Freq" = "TH1", 
                    "TH1.2.Freq" = "TH1/2", "TH2.Freq" = "TH2", "G_x_x_T"="IFNγ\n&\nTNFa"))
#graph with facets
a<-baseplot(melt[melt$variable!="G_x_x_T",], "SM", "value", ltbi.cols)+
    facet_wrap(~variable, ncol=4, labeller=cyt_groups)+
    labs(y="Frequency of Cytokine+ CD4+ T cells (%)")
b<-baseplot(melt[melt$variable=="G_x_x_T",], "SM", "value", ltbi.cols)+
    facet_wrap(~variable, ncol=4, labeller=cyt_groups)+
    labs(y="")
grid.arrange(a,b, ncol=2, widths=c(3,1))
```

@@

booleanplot(test, "variable", "value", ltbi.cols)+
    scale_x_discrete(labels = labels)+
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=6)+
    labs(y="Frequency of Transcription Factor \n Mtb-Specific TH1 cells (%)")

@@

neg <- cor(lum[lum$SM=="SM-",3:11])
order <- corrMatOrder(neg, order = "hclust", hclust.method="centroid")
order.neg <- neg[order, order]
res1 <- cor.mtest(lum[lum$SM=="SM-",3:11], conf.level = .95)
pvals <- res1$p[order, order]
corrplot(order.neg, method = "circle", insig = "label_sig", tl.col = "black", 
         p.mat = pvals, sig.level = c(.001, .01, .05), pch.cex = .9, pch.col = "white",
         type="upper")

pos <- cor(lum[lum$SM=="SM+",3:11])
order.pos <- pos[order, order]
res1 <- cor.mtest(lum[lum$SM=="SM+",3:11], conf.level = .95)
pvals <- res1$p[order, order]
corrplot(order.pos, method = "circle", insig = "label_sig", tl.col = "black", 
         p.mat = pvals, sig.level = c(.001, .01, .05), pch.cex = .9, pch.col = "white",
         type="upper")

@@

####Similar to the overnight assay, expanded Mtb-specific TH1 cytokine producing cells express both TH1 and TH2 lineage-specific markers, however this does not differ by S. mansoni status.  
*I maybe want to do some analysis about the fact that now higher frequencies of cells express T-bet and/or GATA3 and that there seems to be a preferential expansion of CCR4+ cells but I honestly don't know how to test that*
```{r, fig.height=6, fig.width=10}
#graph phenotype
melt<-melt(ogphen, id.vars=c("TB", "SM"), measure.vars = grep("._._._.", names(ogphen)))
test<-filter(melt, variable!="x_x_x_x")
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" ,       
"t_x_3_x" ,         
"t_x_x_4" ,         
"t_x_x_x" ,
"t_g_3_4" ,         
"t_g_3_x" ,         
"t_g_x_4" ,         
"t_g_x_x" ,
"x_g_3_4" ,         
"x_g_3_x" ,         
"x_g_x_4" ,         
"x_g_x_x" ,
"x_x_3_4" ,          
"x_x_3_x" ,         
"x_x_x_4"           
))

@@

booleanplot(test, "variable", "value", ltbi.cols)+
    scale_x_discrete(labels = labels)+
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=6)+
    labs(y="Frequency of Transcription Factor \n Mtb-Specific CD4+ T cells (%)")
```

@@

#generate cytokine table for graphing
melt<-melt(cyt, 
    id.vars=c("TB","SM"), 
    measure.vars=c("Cyt.Freq", "TH1.Freq", "TH1.2.Freq", "TH2.Freq"))
cyt_groups <- as_labeller(c("Cyt.Freq" = "Total", "TH1.Freq" = "TH1", 
                    "TH1.2.Freq" = "TH1/2", "TH2.Freq" = "TH2"))
#graph cytokine with facets
baseplot(melt, "SM", "value", tb.cols)+
    facet_wrap(~variable, ncol=4, labeller=cyt_groups)+
    labs(y="Frequency of Cytokine+ \nCD4+ T cells (%)")
```

@@

booleanplot(test, "variable", "value", tb.cols)+
    scale_x_discrete(labels = labels)+
    labs(y="Frequency of Transcription Factor \n Mtb-Specific TH1 cells (%)")

booleanplot(test[grep("g", test$variable),], "variable", "value", tb.cols)+
    scale_x_discrete(labels = labels[5:12])+
    labs(y="Frequency of Transcription Factor \n Mtb-Specific TH1 cells (%)")

>>>>

---
title: "Paper Figures"
author: "Taryn McLaughlin"
date: "7/29/2019"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, comment=NA, warning=FALSE, echo=FALSE)
library(dplyr)
library(knitr)
library(ggplot2)
library(gridExtra)
library(GGally)
library(ggpubr)
library(cowplot)
library(tidyr)
library(reshape2)
library(cowplot)
library(corrplot)
library(sjPlot)
```

@@

baseplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ theme(legend.position="none")+
    theme(text = element_text(size=20))+
    theme(plot.subtitle = element_text(hjust = 0.5)) +
    stat_compare_means(
        label="p.signif", hide.ns = TRUE, size=8,
        label.x=1.3,
        label.y = boxplot.stats(data[,yval])$stats[5]*1.4)+
    coord_cartesian(ylim=c(0, boxplot.stats(data[,yval])$stats[5]*1.5))+
    labs(x="", y="")
}

booleanplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none")+
    theme(text = element_text(size=20))+
    theme(plot.subtitle = element_text(hjust = 0.5)) +
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=8)+
    labs(x="", y="")
}

allplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=disease))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    scale_x_discrete(labels=c("HC\nSM-", "HC\nSM+", "LTBI\nSM-", "LTBI\nSM+", "TB\nSM-", "TB\nSM+"))+
    theme(legend.position="none")+
    theme(text = element_text(size=20))+
    theme(plot.subtitle = element_text(hjust = 0.5)) +
    stat_compare_means(
        comparisons = list(c("HC SM+", "HC SM-"),c("LTBI SM+", "LTBI SM-"), c("TB SM+", "TB SM-")),
        label="p.signif", hide.ns = TRUE, size=8,
        label.y = boxplot.stats(data[,yval])$stats[5]*1.4)+
        coord_cartesian(ylim=c(0, boxplot.stats(data[,yval])$stats[5]*1.5))+
        labs(x="", y="")
}

all_comps<-list(c("HC SM+", "HC SM-"),c("LTBI SM+", "LTBI SM-"), c("TB SM+", "TB SM-"))

healthy.cols<- c("SM+" = "#1a9850", "SM-" ="#91cf60")
ltbi.cols<- c("SM+" = "#2166ac", "SM-" = "#85ABD1")
tb.cols<- c("SM+" = "#b2182b", "SM-"="#E59EA6")
all.cols<- c("HC SM+" = "#1a9850", "HC SM-" ="#91cf60",
             "LTBI SM+" = "#2166ac", "LTBI SM-" = "#85ABD1",
             "TB SM+" = "#b2182b", "TB SM-"="#E59EA6")
```

@@

#All groups
```{r, fig.height=6, fig.width=3}
cd4<-plot_filter(subset(CD4, CD4$Stim=="UN"))
cyt<-plot_filter(subset(CYT, CYT$Stim=="PMA"))
phen<-plot_filter(subset(PHEN, PHEN$Stim=="PMA"))
og<-plot_filter(subset(OG, OG$Stim=="SEB"))
ogphen<-plot_filter(subset(OGPHEN, OGPHEN$Stim=="SEB"))
```

```{r, fig.width=16, fig.height=8}
melt<-melt(cd4, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3", "CXCR3", "CCR4"))

a<-allplot(melt[melt$variable=="T-bet",], "disease", "value", all.cols)+    
    facet_wrap(~variable)+
    labs(y="(%) Total CD4+ T cells")

b<-allplot(melt[melt$variable=="GATA3",], "disease", "value", all.cols)+    
    facet_wrap(~variable)

c<-allplot(melt[melt$variable=="CXCR3",], "disease", "value", all.cols)+    
    facet_wrap(~variable)

d<-allplot(melt[melt$variable=="CCR4",], "disease", "value", all.cols)+    
    facet_wrap(~variable)

cowplot::plot_grid(a, b, c, d,ncol=4)
```

```{r, fig.width=16, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa", "IL4", "IL13"))
cyt_groups <- as_labeller(c("IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4", "IL13" = "IL-13"))

a<-allplot(melt[melt$variable=="IFNg",], "disease", "value", all.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    labs(y="Frequency of Cytokine+ CD4+ T cells (%)")

b<-allplot(melt[melt$variable=="TNFa",], "disease", "value", all.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

c<-allplot(melt[melt$variable=="IL4",], "disease", "value", all.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

d<-allplot(melt[melt$variable=="IL13",], "disease", "value", all.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

cowplot::plot_grid(a, b, c, d,ncol=4)
```

#Healthy Adults
####The frequency of T-bet+ CD4+ T cells is lower amongst SM+ Healthy Adults  
```{r, fig.height=6, fig.width=3}
cd4<-filter_hc(subset(CD4, CD4$Stim=="UN"))
cyt<-filter_hc(subset(CYT, CYT$Stim=="PMA"))
phen<-filter_hc(subset(PHEN, PHEN$Stim=="PMA"))
og<-filter_hc(subset(OG, OG$Stim=="SEB"))
ogphen<-filter_hc(subset(OGPHEN, OGPHEN$Stim=="SEB"))
```

####Generic cytokine production from CD4+ T cells stimulated with PMA & Ionomycin does not differ between SM- and SM+ Healthy Adults
```{r, fig.height=6, fig.width=10}
melt<-melt(cyt, id.vars=c("TB","SM"), measure.vars=c("TH1.Freq", "TH1.2.Freq", "TH2.Freq"))
cyt_groups <- as_labeller(c("TH1.Freq" = "TH1", 
                    "TH1.2.Freq" = "TH1/2", "TH2.Freq" = "TH2"))
baseplot(melt, "SM", "value", healthy.cols)+
    facet_wrap(~variable, ncol=4, labeller=cyt_groups)+
    labs(y="Frequency of Cytokine+ CD4+ T cells (%)")
```

@@

```{r, fig.height=10, fig.width=5}
test<-melt(phen, id.vars=c("TB", "SM"), 
           measure.vars=c("TH1_T-bet", "TH1_GATA3", "TH1_CXCR3", "TH1_CCR4",
           "TH2_T-bet", "TH2_GATA3", "TH2_CXCR3", "TH2_CCR4"))

test$subset<-tstrsplit(test$variable, "_")[[1]]
test$subset<-paste(test$subset, "Cytokine+\nCD4+ T Cells", sep=" ")
test$variable<-gsub("TH1_","", test$variable)
test$variable<-gsub("TH2_","", test$variable)
test$variable<-factor(test$variable, levels=c("T-bet", "GATA3", "CXCR3", "CCR4"))

@@

#LTBI

####LTBI individuals coinfected with S. mansoni have higher Mtb peptide-specific total cytokine production, specifically due to higher co-production of IFNγ and TNFa
```{r, fig.height=6, fig.width=10}
cyt<-filter_ltbi(subset(CYT, CYT$Stim=="PEP"))
phen<-filter_ltbi(subset(PHEN, PHEN$Stim=="PEP"))
og<-filter_ltbi(subset(OG, OG$Stim=="PEP"))
ogphen<-filter_ltbi(subset(OGPHEN, OGPHEN$Stim=="PEP"))
oggt<-filter_ltbi(subset(OG.GT, OG.GT$Stim=="PEP"))

#generate cytokine table for graphing
melt<-melt(cyt, 
    id.vars=c("TB","SM"), 
    measure.vars=c("Cyt.Freq", "TH1.Freq", "TH1.2.Freq", "TH2.Freq", "G_x_x_T"))
cyt_groups <- as_labeller(c("Cyt.Freq" = "Total", "TH1.Freq" = "TH1", 
                    "TH1.2.Freq" = "TH1/2", "TH2.Freq" = "TH2", "G_x_x_T"="IFNγ\n&\nTNFa"))
#graph with facets
a<-baseplot(melt[melt$variable!="G_x_x_T",], "SM", "value", ltbi.cols)+
    facet_wrap(~variable, ncol=4, labeller=cyt_groups)+
    labs(y="Frequency of Cytokine+ CD4+ T cells (%)")
b<-baseplot(melt[melt$variable=="G_x_x_T",], "SM", "value", ltbi.cols)+
    facet_wrap(~variable, ncol=4, labeller=cyt_groups)+
    labs(y="")
```

```{r, fig.width=16, fig.height=8}
melt<-melt(cd4, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3", "CXCR3", "CCR4"))

a<-baseplot(melt[melt$variable=="T-bet",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    labs(y="(%) Total CD4+ T cells")

b<-baseplot(melt[melt$variable=="GATA3",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable)

c<-baseplot(melt[melt$variable=="CXCR3",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable)

d<-baseplot(melt[melt$variable=="CCR4",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable)

cowplot::plot_grid(a, b, c, d,ncol=4)
```

```{r, fig.width=16, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa", "IL4", "IL13"))
cyt_groups <- as_labeller(c("IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4", "IL13" = "IL-13"))

a<-baseplot(melt[melt$variable=="IFNg",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    labs(y="Frequency of Cytokine+ CD4+ T cells (%)")

b<-baseplot(melt[melt$variable=="TNFa",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

c<-baseplot(melt[melt$variable=="IL4",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

d<-baseplot(melt[melt$variable=="IL13",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

cowplot::plot_grid(a, b, c, d,ncol=4)
```

```{r, fig.height=6, fig.width=10}
#generate cytokine table for graphing
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa", "IL4", "IL13"))
cyt_groups <- as_labeller(c("IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4", "IL13" = "IL-13"))
#graph with facets
baseplot(melt, "SM", "value", ltbi.cols)+
    facet_wrap(~variable, ncol=4, labeller=cyt_groups)+
    labs(y="Frequency of Cytokine+ CD4+ T cells (%)")
```

@@

@@

neg <- cor(lum[lum$SM=="SM-",3:11])
order <- corrMatOrder(neg, order = "hclust", hclust.method="centroid")
order.neg <- neg[order, order]
res1 <- cor.mtest(lum[lum$SM=="SM-",3:11], conf.level = .95)
pvals <- res1$p[order, order]
corrplot(order.neg, method = "circle", insig = "label_sig", tl.col = "black", 
         p.mat = pvals, sig.level = c(.001, .01, .05), pch.cex = 2, pch.col = "white",
         type="upper")

pos <- cor(lum[lum$SM=="SM+",3:11])
order.pos <- pos[order, order]
res1 <- cor.mtest(lum[lum$SM=="SM+",3:11], conf.level = .95)
pvals <- res1$p[order, order]
corrplot(order.pos, method = "circle", insig = "label_sig", tl.col = "black", 
         p.mat = pvals, sig.level = c(.001, .01, .05), pch.cex = 2, pch.col = "white",
         type="upper")

@@

####Similar to the overnight assay, expanded Mtb-specific TH1 cytokine producing cells express both TH1 and TH2 lineage-specific markers, however this does not differ by S. mansoni status.

*I maybe want to do some analysis about the fact that now higher frequencies of cells express T-bet and/or GATA3 and that there seems to be a preferential expansion of CCR4+ cells but I honestly don't know how to test that*
```{r, fig.height=6, fig.width=10}
#graph phenotype
melt<-melt(ogphen, id.vars=c("TB", "SM"), measure.vars = grep("._._._.", names(ogphen)))
test<-filter(melt, variable!="x_x_x_x")
test$variable<-factor(test$variable, levels=c(
"t_x_3_4" ,       
"t_x_3_x" ,         
"t_x_x_4" ,         
"t_x_x_x" ,
"t_g_3_4" ,         
"t_g_3_x" ,         
"t_g_x_4" ,         
"t_g_x_x" ,
"x_g_3_4" ,         
"x_g_3_x" ,         
"x_g_x_4" ,         
"x_g_x_x" ,
"x_x_3_4" ,          
"x_x_3_x" ,         
"x_x_x_4"           
))

@@

booleanplot(test, "variable", "value", ltbi.cols)+facet_wrap(~tf, scales="free", ncol=4)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=6)+
    labs(y="Frequency of Transcription Factor \n Mtb-Specific TH1 cells (%)")
```

@@

#generate cytokine table for graphing
melt<-melt(cyt, 
    id.vars=c("TB","SM"), 
    measure.vars=c("TH1.Freq", "TH1.2.Freq", "TH2.Freq"))
cyt_groups <- as_labeller(c("TH1.Freq" = "TH1", 
                    "TH1.2.Freq" = "TH1/2", "TH2.Freq" = "TH2"))
#graph cytokine with facets
keep <- baseplot(melt, "SM", "value", tb.cols)+
    facet_wrap(~variable, ncol=4, labeller=cyt_groups)+
    labs(y="Frequency of Cytokine+ \nCD4+ T cells (%)")
```

```{r, fig.width=16, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa", "IL4", "IL13"))
cyt_groups <- as_labeller(c("IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4", "IL13" = "IL-13"))

a<-baseplot(melt[melt$variable=="IFNg",], "disease", "value", tb.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    labs(y="Frequency of Cytokine+ CD4+ T cells (%)")

b<-baseplot(melt[melt$variable=="TNFa",], "disease", "value", tb.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

c<-baseplot(melt[melt$variable=="IL4",], "disease", "value", tb.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

d<-baseplot(melt[melt$variable=="IL13",], "disease", "value", tb.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

cowplot::plot_grid(a, b, c, d,ncol=4)
```

@@
